Figures and results for main manuscript

### 2020-08-04 analysis/reports/manuscript_main.Rmd
removing smaller than 50 does not change

ggplot(all_di, aes(x = log_s0, y = log_n0, color = dat)) +
  geom_point(alpha = .4) +
  theme_bw() +
  scale_color_viridis_d() +
  ggtitle("Communities by S and N")

@@

ggplot(all_di, aes(simpson_percentile)) + 
 geom_histogram(bins = 100) +
  geom_vline(xintercept = 5, color = "red") +
  theme_bw() +
  facet_wrap(vars(dat), scales = "free_y") + ggtitle("Evenness, all sites")
```

@@

@@

fia_sized <- filter(all_di, s0 <= fia_max_s,n0 <= fia_max_n) %>%
  mutate(fia_yn = dat == "fia") %>%
  mutate(fia_yn = ifelse(fia_yn, "FIA", "Other datasets"))

ggplot(filter(fia_sized, s0 > 2, nparts > 10), aes(skew_percentile)) +
  geom_histogram() +
  facet_wrap(vars(fia_yn), scales = "free_y")

ggplot(filter(fia_sized, s0 > 2, log_nparts > 5, nparts > 10), aes(skew_percentile)) +
  geom_histogram() +
  facet_wrap(vars(fia_yn), scales = "free_y")

ggplot(filter(fia_sized, s0 > 2, log_nparts <  5, nparts > 10), aes(skew_percentile)) +
  geom_histogram(bins = 100) +
  facet_wrap(vars(fia_yn), scales = "free_y")

@@

>>>>

ggplot(all_di, aes(x = log_s0, y = log_n0, color = dat)) +
  geom_point(alpha = .01) +
  geom_point(data = filter(all_di, log_nparts > log(50)), alpha = .4) +
  theme_bw() +
  scale_color_viridis_d() +
  ggtitle("Communities by S and N")

@@

ggplot(filter(all_di, s0 > 2, log_nparts > log(50)), aes(skew_percentile)) +
  geom_histogram(bins = 100) +
  geom_vline(xintercept = 95, color = "red") +
  theme_bw() +
  facet_wrap(vars(dat), scales = "free_y") + ggtitle("Skewness, all sites")

ggplot(all_di, aes(simpson_percentile)) + 
 geom_histogram(bins = 100) +
  geom_vline(xintercept = 5, color = "red") +
  theme_bw() +
  facet_wrap(vars(dat), scales = "free_y") + ggtitle("Evenness, all sites")
ggplot(filter(all_di, log_nparts > log(50)), aes(simpson_percentile)) + 
 geom_histogram(bins = 100) +
  geom_vline(xintercept = 5, color = "red") +
  theme_bw() +
  facet_wrap(vars(dat), scales = "free_y") + ggtitle("Evenness, all sites")
```

@@

overall_skew_results2 <- all_di %>%
  filter(s0 > 2, log_nparts > log(50)) %>%
  mutate(high_skew = skew_percentile > 95) %>%
  group_by(dat) %>%
  summarize(proportion_skew_high = mean(high_skew),
            nsites_skew = dplyr::n())

overall_simpson_results2 <- all_di %>%
  filter(log_nparts > log(50)) %>%
  mutate(low_even = simpson_percentile < 5) %>%
  group_by(dat) %>%
  summarize(proportion_even_low = mean(low_even),
            nsites_even = dplyr::n())

overall_results2 <- left_join(overall_skew_results2, overall_simpson_results2)

overall_results2

@@

fia_max_nparts <-max(filter(all_di, dat == "fia")$log_nparts)

fia_sized <- filter(all_di, s0 <= fia_max_s, n0 <= fia_max_n) %>%
  mutate(fia_yn = dat == "fia") %>%
  mutate(fia_yn = ifelse(fia_yn, "FIA", "Other datasets")) %>%
  mutate(right_corner = FALSE)

ggplot(filter(fia_sized, s0 > 2, nparts > 50), aes(skew_percentile)) +
  geom_histogram() +
  facet_wrap(vars(fia_yn), scales = "free_y")

ggplot(fia_sized, aes(x = log_nparts)) +
  geom_histogram() +
  facet_wrap(vars(fia_yn), scales = "free_y") +
  geom_vline(xintercept = log(50))

ggplot(fia_sized, aes(s0, n0, color = fia_yn)) +
  geom_point()

@@

ggplot(filter(fia_sized, s0 > 2, nparts > 50, nparts < exp(7)), aes(skew_percentile)) +
  geom_histogram() +
  facet_wrap(vars(fia_yn), scales = "free_y") +
  ggtitle("50-1,000 parts in FS")

ggplot(filter(fia_sized, s0 > 2, nparts > 50, nparts >= exp(7)), aes(skew_percentile)) +
  geom_histogram() +
  facet_wrap(vars(fia_yn), scales = "free_y") +
  ggtitle("More than 1,000 parts in FS")

ggplot(filter(fia_sized, s0 > 2, nparts > 50, nparts >= exp(10)), aes(skew_percentile)) +
  geom_histogram() +
  facet_wrap(vars(fia_yn), scales = "free_y") +
  ggtitle("More than 20,000 parts in FS")
```
